---
title: "Plotly and flexdashboard"
author: "Karina Myers"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

focusing on airbnb data for this topic
select a few of the vraiables, filter to include a subset of data

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

## Plotly scatter plot

There are several practical differences comparing ggplot and plot_ly but the underlying conceptual framework is similar. Define a dataset, specify how variables map to plot elements, pick a plot type. 

Plot the location of the retnals in our datset. map price to color. 
the type of plot is scatter which has sever "modes": 
  - markers produce the same type of plot ggplot::geom_point
  - lines produces the same kind of plot as ggplot::geom_line

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```
This is useful since it gives additional info and allows you to hover and zoom in/out

## Plotly boxplot 
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

## Plotly Barchar
Plotly expects data in a specific format for bar charts, so we use count to get the numb of rentals in each neighborhood (ie bar to the right). 
```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

## Ggplotly 
You can convert a ggplot object straight to an interactive graphic using ggplotly 

```{r}
scatter_ggplot = 
  nyc_airbnb %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

recreating our boxplot 
```{r}
box_ggplot = 
  nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price, fill = neighbourhood)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplotly(box_ggplot)
```

## Flexdashboard 
clearly you can embed interactive graphics in HTML files produced by R markdown. Dashboards are a collection of related graphics (or tables or other outputs) that are displayed in a structured way that's easy to navigate 







